Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Minor changes

  \item Let~$K_0(\cat ; T)$ \yann{I do not like this notation anymore: $K_0(\cat ; T)$ depends on the choice of a CTO $T$. How about $K_0^T(\cat)$, $K_0^{(\susp T)}(\cat)$, $K_0(\cat;T)$, $\Kg(\cat;T)$ or $K_0(\cat;(\susp T))$?}\pg{Good point.  I like~$K_0^T(\cat)$ and~$K_0(\cat;T)$.} be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
  \[
   X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X
  \]
  with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
 \end{enumerate}

>>>>

  \item Let~$K_0(\cat ; T)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
  \[
   X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X
  \]
  with~$h\in (\susp T)$.  Denote by~$\b g:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
 \end{enumerate}
